KidsAIR initial SUMs data work

### 2020-05-13 home_char_act_cleaning.Rmd
data merging updates start on manuscript tables

# Clean up all home characteristics data
```{r}
kids_home_char <- read_rds("Output/kids_home_char.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

@@

# write_rds(home_char_clean, "Output/home_char_clean.rds")
```

@@

# Clean up all home activity data
```{r}
kids_home_act <- read_rds(paste0(file_path, "Output/kids_home_act.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

@@

# write_rds(home_act_clean, paste0(file_path, "Output/home_act_clean.rds"))
```

>>>>

# Clean up all home characteristics data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_home_char <- read_rds(paste0(file_path, "Output/kids_home_char.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

@@

write_rds(home_char_clean, paste0(file_path, "Output/home_char_clean.rds"))
```

@@

# Clean up all home activity data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_home_act <- read_rds(paste0(file_path, "Output/kids_home_act.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

@@

write_rds(home_act_clean, paste0(file_path, "Output/home_act_clean.rds"))
```

### 2020-05-13 indoor_temp_rh_cleaning.Rmd
data merging updates start on manuscript tables

# Clean up all temp/rh data
```{r}
kids_indoor_temp_rh <- read_rds("Output/kids_indoor_temp_rh.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

@@

# write_rds(indoor_temp_rh_clean, "Output/indoor_temp_rh_clean.rds")
```

>>>>

# Clean up all temp/rh data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_indoor_temp_rh <- read_rds(paste0(file_path, "Output/kids_indoor_temp_rh.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

@@

write_rds(indoor_temp_rh_clean, paste0(file_path, "Output/indoor_temp_rh_clean.rds"))
```

### 2020-05-13 merge_datasets.Rmd
data merging updates start on manuscript tables

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(lme4)
library(lmerTest)
```

@@

analysis_data6 <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  mutate(winter_id = as.character(winter_id)) %>%
  select(area, home, home_winter_id, winter_id, treatment, stove_grade) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  right_join(analysis_data5, by = c("area", "home", "home_winter_id", 
                                    "winter_id", "treatment")) %>% 
  mutate(stove_grade_3level = fct_collapse(stove_grade,
                                    "A" = "A",
                                    "C" = "C",
                                    "D or F" = c("D", "F"))) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

@@

# Convert medium data to short: only keeping 1 observation per sampling period, repeated by child_id
```{r}
exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- exposure_analysis_data_medium %>% 
  arrange(area, home, winter_id) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  # Sum home activity vars over entire sampling period to make 1 obs per sampling period
  mutate(home_act_gas = factor(home_act_gas, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_gas = as.character(home_act_gas),
         home_act_gas = as.numeric(home_act_gas),
         home_act_gas_sum = sum(home_act_gas),
         home_act_elect = factor(home_act_elect, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_elect = as.character(home_act_elect),
         home_act_elect = as.numeric(home_act_elect),
         home_act_elect_sum = sum(home_act_elect),
         home_act_propane = factor(home_act_propane, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_propane = as.character(home_act_propane),
         home_act_propane = as.numeric(home_act_propane),
         home_act_propane_sum = sum(home_act_propane),
         home_act_oil = factor(home_act_oil, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_oil = as.character(home_act_oil),
         home_act_oil = as.numeric(home_act_oil),
         home_act_oil_sum = sum(home_act_oil),
         home_act_other = factor(home_act_other, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_other = as.character(home_act_other),
         home_act_other = as.numeric(home_act_other),
         home_act_other_sum = sum(home_act_other),
         home_act_smoking = factor(home_act_smoking, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_smoking = as.character(home_act_smoking),
         home_act_smoking = as.numeric(home_act_smoking),
         home_act_smoking_sum = sum(home_act_smoking),
         home_act_incense = factor(home_act_incense, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_incense = as.character(home_act_incense),
         home_act_incense = as.numeric(home_act_incense),
         home_act_incense_sum = sum(home_act_incense),
         home_act_candle = factor(home_act_candle, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_candle = as.character(home_act_candle),
         home_act_candle = as.numeric(home_act_candle),
         home_act_candle_sum = sum(home_act_candle),
         home_act_kerosene = factor(home_act_kerosene, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_kerosene = as.character(home_act_kerosene),
         home_act_kerosene = as.numeric(home_act_kerosene),
         home_act_kerosene_sum = sum(home_act_kerosene),
         home_act_windows = factor(home_act_windows, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_windows = as.character(home_act_windows),
         home_act_windows = as.numeric(home_act_windows),
         home_act_windows_sum = sum(home_act_windows),
         home_act_door = factor(home_act_door, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_door = as.character(home_act_door),
         home_act_door = as.numeric(home_act_door),
         home_act_door_sum = sum(home_act_door),
         home_act_sweep = factor(home_act_sweep, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_sweep = as.character(home_act_sweep),
         home_act_sweep = as.numeric(home_act_sweep),
         home_act_sweep_sum = sum(home_act_sweep)) %>% 
  group_by(area, home, winter_id) %>% 
  distinct(child_id_char, .keep_all = TRUE) %>% 
  ungroup() %>% 
  arrange(area, home, winter_id)

>>>>

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
```

@@

analysis_data6 <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  mutate(winter_id = as.character(winter_id)) %>%
  select(area, home, home_winter_id, winter_id, treatment, stove_grade) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  right_join(analysis_data5, by = c("area", "home", "home_winter_id", 
                                    "winter_id", "treatment")) %>% 
  mutate(stove_grade_3level = fct_collapse(stove_grade,
                                    "A" = "A",
                                    "C" = "C",
                                    "F" = c("D", "F"))) %>% 
  ungroup() %>% 
  arrange(area, home, home_winter_id, sample_date)

@@

# Convert medium data to short: only keeping 1 observation per sampling period, repeated by child_id
```{r}
exposure_analysis_data_medium <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_medium.rds"))
exposure_analysis_data_long <- 
  read_rds(paste0(output_path, "Output/exposure_analysis_data_long_new.rds")) 
sums_rolling_pm_data <- 
  read_rds(paste0(output_path, "Output/sums_rolling_pm_data.rds"))

####### Format SUMs data to merge with analysis data below
sums_temp_change <- sums_rolling_pm_data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home, sampling_day) %>% 
  distinct(datetime_sums, .keep_all = TRUE) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(time_diff = (lead(datetime_sums) - datetime_sums)) %>% 
  mutate(lead_temp = if_else(time_diff < 20, lead(temp_c_sums, 4), lead(temp_c_sums)),
         lead_temp = if_else(time_diff > 25, 999, lead_temp)) %>% 
  replace_with_na(replace = list(lead_temp = 999)) %>% 
  mutate(temp_diff = lead_temp - temp_c_sums,
         # change temp in the following line
         temp_diff_check = if_else(temp_diff >= 5, 1, 0),
         heat_event = if_else(temp_diff_check == 1 & lag(temp_diff_check) == 1, 0,
                              temp_diff_check),
         heat_event = if_else(is.na(temp_diff_check), 1,
                              heat_event)) %>% 
  group_by(area, home, sampling_day) %>% 
  mutate(sums_events_sampling_day = sum(heat_event, na.rm = TRUE),
         sums_events_sampling_day_cat = cut(sums_events_sampling_day, 
                                            breaks = c(0, 2, 50),
                           labels = c("<2", "2+"),
                                 right = FALSE)) %>% 
  distinct(sampling_day, .keep_all = TRUE) %>% 
  ungroup() %>% 
  select(area:pm_rolling_20, sums_mean_winter:sums_mean_sampling_period,
         time_diff:sums_events_sampling_day_cat) %>% 
  arrange(area, home, sample_date) %>% 
  group_by(home) %>% 
  mutate(sums_events_sampling_period = mean(sums_events_sampling_day, na.rm = TRUE)) %>% 
  select(area, home, home_winter_id, sums_events_sampling_period) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

####### Format ambient data to merge with analysis data below
ambient_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1) %>% 
  filter(treatment == "Placebo") %>% 
  #filter(area == "WMT") %>%
  filter(!is.na(sampling_day)) %>% 
  filter(!is.na(sample_date)) %>%
  select(area, home, child_id_char, sample_date, sampling_day, pm_mean_daily,
         amb_pm_24hr:mean_temp_roll_4day) %>% 
  group_by(home) %>% 
  mutate(amb_pm_sampling_period_5 = mean(amb_pm_24hr, na.rm = TRUE)/5,
         mean_temp_sampling_period_5 = mean(mean_temp, na.rm = TRUE)/5) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  replace_with_na(replace = list(mean_temp_sampling_period_5 = "NaN")) %>% 
  replace_with_na(replace = list(amb_pm_sampling_period_5 = "NaN")) %>% 
  select(area, home, mean_temp_sampling_period_5, amb_pm_sampling_period_5)

exposure_analysis_data_short <- exposure_analysis_data_medium %>% 
  arrange(area, home, winter_id) %>% 
  group_by(area, home, winter_id, child_id_char) %>% 
  # Sum home activity vars over entire sampling period to make 1 obs per sampling period
  mutate(home_act_gas = factor(home_act_gas, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_gas = as.character(home_act_gas),
         home_act_gas = as.numeric(home_act_gas),
         home_act_gas_sum = sum(home_act_gas),
         home_act_elect = factor(home_act_elect, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_elect = as.character(home_act_elect),
         home_act_elect = as.numeric(home_act_elect),
         home_act_elect_sum = sum(home_act_elect),
         home_act_propane = factor(home_act_propane, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_propane = as.character(home_act_propane),
         home_act_propane = as.numeric(home_act_propane),
         home_act_propane_sum = sum(home_act_propane),
         home_act_oil = factor(home_act_oil, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_oil = as.character(home_act_oil),
         home_act_oil = as.numeric(home_act_oil),
         home_act_oil_sum = sum(home_act_oil),
         home_act_other = factor(home_act_other, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_other = as.character(home_act_other),
         home_act_other = as.numeric(home_act_other),
         home_act_other_sum = sum(home_act_other),
         home_act_smoking = factor(home_act_smoking, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_smoking = as.character(home_act_smoking),
         home_act_smoking = as.numeric(home_act_smoking),
         home_act_smoking_sum = sum(home_act_smoking),
         home_act_incense = factor(home_act_incense, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_incense = as.character(home_act_incense),
         home_act_incense = as.numeric(home_act_incense),
         home_act_incense_sum = sum(home_act_incense),
         home_act_candle = factor(home_act_candle, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_candle = as.character(home_act_candle),
         home_act_candle = as.numeric(home_act_candle),
         home_act_candle_sum = sum(home_act_candle),
         home_act_kerosene = factor(home_act_kerosene, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_kerosene = as.character(home_act_kerosene),
         home_act_kerosene = as.numeric(home_act_kerosene),
         home_act_kerosene_sum = sum(home_act_kerosene),
         home_act_windows = factor(home_act_windows, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_windows = as.character(home_act_windows),
         home_act_windows = as.numeric(home_act_windows),
         home_act_windows_sum = sum(home_act_windows),
         home_act_door = factor(home_act_door, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_door = as.character(home_act_door),
         home_act_door = as.numeric(home_act_door),
         home_act_door_sum = sum(home_act_door),
         home_act_sweep = factor(home_act_sweep, levels = c("Yes", "No"), labels = c(1, 0)), 
         home_act_sweep = as.character(home_act_sweep),
         home_act_sweep = as.numeric(home_act_sweep),
         home_act_sweep_sum = sum(home_act_sweep)) %>% 
  group_by(area, home, winter_id) %>% 
  distinct(child_id_char, .keep_all = TRUE) %>% 
  ungroup() %>% 
  left_join(sums_temp_change, by = c("area", "home", "home_winter_id")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  arrange(area, home, winter_id)

### 2020-05-13 merge_health_datasets.Rmd
health data cleaning
data merging updates start on manuscript tables

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 14 April 2020"
output: pdf_document
---

@@

at_home_pm_merged <- 
  read_rds(paste0(output_path, "Output/at_home_pm_merged.rds"))
kids_med_visit <- 
  read_rds(paste0(output_path, "Output/kids_med_visit.rds")) %>% 
  mutate(visit_date = med_visit_date) 
kids_birth_infancy <- 
  read_rds(paste0(output_path, "Output/kids_birth_infancy.rds")) %>% 
  select(-home_id)
child_home_winter <- 
  read_rds(paste0(output_path, "Output/child_home_winter.rds")) %>% 
  select(-home_id.x, -home_id.y, -chw_symptom_free_date)
kids_csq <- 
  read_rds(paste0(output_path, "Output/kids_csq.rds"))
kids_lrti <- 
  read_rds(paste0(output_path, "Output/kids_lrti.rds")) %>% 
  select(-home_id)
kids_medical_records <- 
  read_rds(paste0(output_path, "Output/kids_medical_records.rds")) %>% 
  select(-visit_date)
```

@@

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period, day_of_week) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  left_join(exposure_analysis_data_medium,
            by = c("area", "home", "home_winter_id", "winter_id", "treatment",
                   "child_id_num", "sampling_day"))

#write_rds(health_exposure_data_sampling_day, paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))
#write_csv(health_exposure_data_sampling_day, paste0(output_path, "Output/health_exposure_data_sampling_day.csv"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))

>>>>

---
title: "KidsAIR: merge health datasets"
author: "Ethan Walker"
date: "Started 27 March 2020, Updated 22 April 2020"
output: pdf_document
---

@@

at_home_pm_merged <- 
  read_rds(paste0(output_path, "Output/at_home_pm_merged.rds"))
kids_med_visit <- 
  read_rds(paste0(output_path, "Output/kids_med_visit.rds")) %>% 
  mutate(visit_date = med_visit_date) 
kids_birth_infancy <- 
  read_rds(paste0(output_path, "Output/kids_birth_infancy.rds")) %>% 
  select(-home_id)
child_home_winter <- 
  read_rds(paste0(output_path, "Output/child_home_winter.rds")) %>% 
  select(-home_id.x, -home_id.y, -chw_symptom_free_date)
kids_csq <- 
  read_rds(paste0(output_path, "Output/kids_csq.rds"))
kids_lrti <- 
  read_rds(paste0(output_path, "Output/kids_lrti.rds")) %>% 
  select(-home_id) %>% 
  mutate(winter_id = as.character(winter_id))
kids_medical_records <- 
  read_rds(paste0(output_path, "Output/kids_medical_records.rds")) %>% 
  select(-visit_date)
```

@@

health_exposure_data_sampling_day <- health_data_merged %>% 
  select(-pm_mean_sampling_day, -pm_mean_sampling_period, day_of_week) %>% 
  mutate(winter_id = as.character(winter_id)) %>% 
  right_join(exposure_analysis_data_medium,
            by = c("area", "home", "home_winter_id", "winter_id", "treatment",
                   "child_id_num", "sampling_day"))

write_rds(health_exposure_data_sampling_day, paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))
write_csv(health_exposure_data_sampling_day, paste0(output_path, "Output/health_exposure_data_sampling_day.csv"))
```

```{r}
health_exposure_data_sampling_day <- 
  read_rds(paste0(output_path, "Output/health_exposure_data_sampling_day.rds"))

### 2020-05-13 moisture_data_cleaning.Rmd
data merging updates start on manuscript tables

# Clean up all moisture data
```{r}
kids_moisture <- read_rds("Output/kids_moisture.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

@@

# write_rds(moisture_clean, "Output/moisture_clean.rds")
```

>>>>

# Clean up all moisture data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_moisture <- read_rds(paste0(file_path, "Output/kids_moisture.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))

@@

write_rds(moisture_clean, paste0(file_path, "Output/moisture_clean.rds"))
```

### 2020-05-13 stove_grade_usage_cleaning.Rmd
data merging updates start on manuscript tables

# Load, format, and save wood stove grade data
```{r}
##### WMT #####
# Load data
stove_grades_initial_wmt <- read_csv("Input/WMT/wmt_stove_grades_20200113.csv")

@@

##### NN #####
# Load data
stove_grades_initial_nn <- read_xlsx("Input/NN/nn_stove_grades_20200113.xlsx")

@@

##### AK #####
# Load data
stove_grades_initial_ak <- read_xlsx("Input/AK/ak_stove_grades_20200113.xlsx")

@@

# Save as RDS
# write_rds(ak_stove_grades, "Output/ak_stove_grades.rds")
```

@@

# Clean up all stove grade data
```{r}
kids_stove_grades <- read_rds("Output/kids_stove_grades.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

stove_grades_clean <- kids_stove_grades %>% 
  filter(home_id != 0) %>% 
  rename(stove_grade_comments = comments) %>% 
  select(-home_id) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

# write_rds(stove_grades_clean, "Output/stove_grades_clean.rds")

@@

# Clean up all stove use data
```{r}
kids_stove_use <- read_rds("Output/kids_stove_use.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds")

@@

# write_rds(stove_use_clean, "Output/stove_use_clean.rds")
```

>>>>

# Load, format, and save wood stove grade data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

##### WMT #####
# Load data
stove_grades_initial_wmt <- read_csv(paste0(file_path, "Input/WMT/wmt_stove_grades_20200113.csv"))

@@

##### NN #####
# Load data
stove_grades_initial_nn <- read_xlsx(paste0(file_path, "Input/NN/nn_stove_grades_20200113.xlsx"))

@@

##### AK #####
# Load data
stove_grades_initial_ak <- read_xlsx(paste0(file_path, "Input/AK/ak_stove_grades_20200113.xlsx"))

@@

# Save as RDS
write_rds(ak_stove_grades, paste0(file_path, "Output/ak_stove_grades.rds"))
```

@@

# Clean up all stove grade data
```{r}
kids_stove_grades <- read_rds(paste0(file_path, "Output/kids_stove_grades.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

stove_grades_clean <- kids_stove_grades %>% 
  filter(home_id != 0) %>% 
  filter(stove_grade != "D") %>% 
  rename(stove_grade_comments = comments) %>% 
  select(-home_id) %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  arrange(area, home, winter_id)

write_rds(stove_grades_clean, paste0(file_path, "Output/stove_grades_clean.rds"))

@@

# Clean up all stove use data
```{r}
kids_stove_use <- read_rds(paste0(file_path, "Output/kids_stove_use.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds"))
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

@@

write_rds(stove_use_clean, paste0(file_path, "Output/stove_use_clean.rds"))
```

### 2020-05-13 sums_data_cleaning.Rmd
data merging updates start on manuscript tables

# Continue cleaning up SUMs data
```{r}
all_sums_filtered <- read_rds("Output/all_sums_filtered.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  select(home_winter_id, area, treatment)

@@

# write_rds(sums_clean, "Output/sums_clean.rds")

@@

sums_clean <- read_rds("Output/sums_clean.rds")

@@

# write_rds(sums_new, "Output/sums_clean.rds")
```

# Plot temp over time for individual home to check for trends visually
```{r}
sums_clean <- read_rds("Output/sums_clean.rds")

@@

# Check to see if there are missing files to search for
## Through 22 Jan 2020, all files are accounted for that are not documented as missing
## Update once data collection is finished in April 2020
```{r}
# Load SUMs data
sums_clean <- read_rds("Output/sums_clean.rds")

@@

# Thresholds for heating events
```{r}
# Load SUMs data
sums_clean <- read_rds("Output/sums_clean.rds")

>>>>

# Continue cleaning up SUMs data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
all_sums_filtered <- read_rds(paste0(file_path, "Output/all_sums_filtered.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids.rds")) %>% 
  select(home_winter_id, area, treatment)

@@

write_rds(sums_clean, paste0(file_path, "Output/sums_clean.rds"))

@@

sums_clean <- read_rds(paste0(file_path, "Output/sums_clean.rds"))

@@

write_rds(sums_new, paste0(file_path, "Output/sums_clean.rds"))
```

# Plot temp over time for individual home to check for trends visually
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
sums_clean <- read_rds(paste0(file_path, "Output/sums_clean.rds"))

@@

# Check to see if there are missing files to search for
## Through 22 Jan 2020, all files are accounted for that are not documented as missing
## Update once data collection is finished in April 2020
```{r}
# Load SUMs data
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
sums_clean <- read_rds(paste0(file_path, "Output/sums_clean.rds"))

@@

# Thresholds for heating events
```{r}
# Load SUMs data
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
sums_clean <- read_rds(paste0(file_path, "Output/sums_clean.rds"))
